COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-09-10 main.tex
Add discussion of figure 3

\subsection{Secular Forcing}

@@

>>>>

\subsection{Secular Forcing}\label{sec:sec_force}

@@

An additional effect that the MMRs have on the orbits of planetesimals is visible in figure \ref{fig:long_ph}. This shows the semimajor axis distribution of planetesimals as a function of longitude of perihelion in the EJ simulation. As discussed in section \ref{sec:sec_force}, the eccentric orbit of Jupiter causes the perihelia of the planetesimal orbits to align with the giant perturber. The mean motion resonances, however, drive the rather vigorous precession of the orbits of planetesimals in their vicinity. Because the timescale of the resonances is much shorter than the timescale for secular forcing, the longitudinal orientations of orbits close to the MMRs are effectively randomized. The dashed horizontal lines in figure \ref{fig:long_ph} indicate the libration width of the MMRs at the forced eccentricity (given by the magnitude of equation \ref{eq:eforced}. The size of the zone of vigorous precession roughly matches the libration width of the MMRs. As will be discussed in the next session, the relative longitudinal orientation of the orbits has important implications for where and when planetesimal collisions occur at a given semimajor axis.
